### 2018-08-29 ms.tex
Fix fig reference.

Routine surveillance data, of disease case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information}.
This data is commonly aggregated, reporting disease case counts that occurred within a certain geographic region defined by a polygon.
This type of data is more sensitive than prevalence surveys in low transmission areas as the entire health system is being used to passively monitor disease risk.
Routine surveillance is also often timely, with reports being released annually or monthly, while large prevalence surveys are performed on a more decadely time scale.
However, the unstructured nature of the data collection means that dealing with biases and data gaps is an ongoing research priority \cite{battle2016treatment, cibulskis2011worldwide}.

@@

\caption{{\bf Input incidence and prevalence data and predicted incidence maps. } The incidence and prevalence data (left) and (spatially) out-of-sample predictions (right) for Indonesia (top) and Senagal (bottom).}
\label{fig1}
\end{figure}

>>>>

Routine surveillance data, of disease case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
This data is commonly aggregated, reporting disease case counts that occurred within a certain geographic region defined by a polygon.
This type of data is more sensitive than prevalence surveys in low transmission areas as typically the entire public health system is being used to passively monitor disease risk \cite{cibulskis2011worldwide}.
Routine surveillance is also often timely, with reports being released annually or monthly, while large prevalence surveys are performed on a more decadely time scale.
However, the unstructured nature of the data collection means that dealing with biases and data gaps is an ongoing research priority \cite{battle2016treatment, cibulskis2011worldwide}.

@@

\caption{{\bf Input incidence and prevalence data and predicted incidence maps. } The incidence and prevalence data (left) and (spatially) out-of-sample predictions (right) for Indonesia (top) and Senagal (bottom).}
\label{fig:data}
\end{figure}
